---
title: "Aides Drug"
author: "Angelica Lopez Esparza"
date: "Summer 2023"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
```

# Introduction
```{r}
charlie<- filter(triUmp, DrugUser=="yes")
```

```{r eval=FALSE}
charlie <- charlie %>%
mutate(across(where(is.character), as.factor))
``` 

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides drug (triUmpsal) is under test in clinical trials. Consider only the DrugUsers, does this drug seem effective?  Hint - use dplyr to obtain that subpopulation with the filter command.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected +  treatment, data= charlie)
barchartGC(~infected + treatment,data=charlie, type="percent")

```




```{r}
library(ggplot2)

# Assuming 'charlie' is your dataframe
# Convert 'infected' and 'treatment' to factors (if they are not already factors)
charlie$infected <- as.factor(charlie$infected)
charlie$treatment <- as.factor(charlie$treatment)

# Define custom colors
my_colors <- c("violet", "violetred")

# Create the side-by-side bar chart with custom colors
ggplot(charlie, aes(x = infected, fill = treatment)) +
  geom_bar(position = "dodge") +
  labs(x = "Infected", y = "Count", fill = "Treatment") +
  scale_fill_manual(values = my_colors) +
  theme_minimal()

```
people who ended up getting aids about 25% of these have taken the drug and about 75% had taken placebo. the overall that didnt get anything didnt take the drug and the other half took the placebo.  

### Numerical Descriptive Results 

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
table2 <- xtabs(~infected + treatment, data=charlie)
rowPerc(table2)
colPerc(table2)
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisq.test(table2)
chisqtestGC(table2)
```


there's a big statistical difference and the p value of 1.2420000000 in this result. although only 25% of people got the treatment and 75% got the placebo, those who had the disease in the 25% had successful results.  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

for this assignment we had to complete the datacamp assignment called data manipulation with dyplyr prior to starting the write up. when finished we opened up posit cloud to put in our forked link and create our workspace. we then put in our credentials changed the name and date and committed that. we then created a code to create our data using "charlie" as our data. afterwards we got our data and opened a helper file cat_cat which is where we got our first graph code from  the options it had for us. we used chat GPT to create a second code for us to try but some were unsuccessful with the data so they removed their code from chat gpt. we explained the graphs and committed. we got out numerical results from the cat_cat file and the same with our inferential code. we compared and wrote up a summary for both. we wrote up our conclussion and commited    
